Biogeography of crop progenitors and wild plant resources during the transition to agriculture in West Asia

### 2024-10-25 analysis/analysis.qmd
Add missing dep

```{r dependencies}
library("dplyr")
library("forcats")
library("fs")
library("furrr")
library("ggplot2")
library("ggspatial")
library("gt")
library("here")
library("parsnip")
library("progressr")
library("purrr")
library("ranger")
library("readr")
library("rgbif")
library("rpaleoclim")
library("sf")
library("stars")
library("stringr")
library("tibble")
library("tidyr")

@@

ggplot() + 
  geom_stars(data = rf_pred) +
  facet_wrap(~period, ncol = 2) +
  scale_fill_batlow(reverse = TRUE) +
  coord_sf(crs = latlong) +
  labs(
    title = "Triticum turgidum dicoccum",
    fill = "Predicted occurrence",
    x = NULL,
    y = NULL
  ) +
  theme(
    plot.title = element_text(face = "italic")
  )
```

>>>>

```{r dependencies}
library("dplyr")
library("forcats")
library("fs")
library("furrr")
library("ggplot2")
library("ggspatial")
library("gt")
library("here")
library("khroma")
library("parsnip")
library("progressr")
library("purrr")
library("ranger")
library("readr")
library("rgbif")
library("rpaleoclim")
library("sf")
library("stars")
library("stringr")
library("tibble")
library("tidyr")

@@

ggplot() + 
  geom_stars(data = rf_pred) +
  facet_wrap(~period, ncol = 3) +
  scale_fill_batlow(reverse = TRUE) +
  coord_sf(crs = latlong) +
  labs(
    title = "Triticum turgidum dicoccum",
    fill = NULL,
    x = NULL,
    y = NULL
  ) +
  theme(
    plot.title = element_text(face = "italic")
  )
```
